---
title: "Analysis and Forecasts"
author: "Vishal & Blake"
date: "July 23, 2016"
output: 
  html_document:
      keep_md:  true
---

### Analyzing and Forecasting Data


* *Setting current working directory to Analysis folder*  
    ```{r echo=FALSE}  
      #getwd()  
      # Setting current working directory to Analysis folder so we can access files in this folder directly.  
      setwd('../Analysis')  
    ```  

* *Loading knitr library*  

```{r echo=FALSE}
#Load knitr and fpp library
library(knitr)
```  

* *Seeting chunk options and reading chunks from R scripts*  
```{r echo=FALSE}
#Setting chunk options before reading R script with knitr chunks.
opts_chunk$set(echo = FALSE, cache=FALSE)

#Read chunks from R Script file here
read_chunk('ChulwalarAnalysis.R')
#read_chunk('Test.R')

```  
  
```{r ChulwalarAnalysis, echo=FALSE}

```  

###Summary functions for lm() and tslm() functions

*Summary of model fitted using lm() function*  
```{r echo=FALSE}
summary(TotalAsIs_lm)
```  
*Summary of model fitted using tslm() function*  
```{r echo=FALSE}
summary(TotalAsIs_tslm)
```  

###Using STL method for decomposition - summary on STL

```{r echo=FALSE}
summary(TotalAsIs_stl)
plot(TotalAsIs_stl, col="black", main="TotalAsIs_stl")

```  

*Plotting trend component that was derived by STL function*
```{r echo=FALSE}
plot(TotalAsIs_stl$time.series[,"trend"], col="black")
```


*Modification of seasonality component*
```{r echo=FALSE}
monthplot(TotalAsIs_stl$time.series[,"seasonal"], main="", ylab="Seasonal")
```

### Correlation with external indicators

The indicators are as follows:

* Monthly Change in Export Price Index (CEPI)
```{r}
plot(CEPI, main="CEPI")
cor(TotalAsIs, CEPI)
```

* Monthly Satisfaction Index (SI) government based data
```{r}  
plot(SIGov, main="SIGov")
cor(TotalAsIs, SIGov)
```  

* Average monthly temperatures in Chulwalar
```{r}
plot(Temperature, main="Temperature")
cor(TotalAsIs, Temperature)
```  

* Monthly births in Chulwalar
```{r}
plot(Births, main="Births")
cor(TotalAsIs, Births)
```  

* Monthly Satisfaction Index (SI) external index 
```{r}
plot(SIExtern, main="SIExtern")
cor(TotalAsIs, SIExtern)
```  

* Yearly Exports from Urbano
```{r}
plot(UrbanoExports, main="UrbanoExports")
cor(TotalAsIs, UrbanoExports)
```  

* Yearly number of Globalisation Party members in Chulwalar
```{r}
plot(GlobalisationPartyMembers, main="GlobalisationPartyMembers")
cor(TotalAsIs, GlobalisationPartyMembers)
```  


* Monthly Average Export Price Index for Chulwalar
```{r}
#plot(AEPI, main="AEPI")
#cor(TotalAsIs, AEPI)
```  

* Monthly Producer Price Index (PPI) for Etel in Chulwalar
```{r}
#plot(PPIEtel, main="PPIEtel")
#cor(TotalAsIs, PPIEtel)
```  


* National Holidays
```{r}
#plot(NationalHolidays, main="NationalHolidays")
#cor(TotalAsIs, NationalHolidays)
```  


* Chulwalar Index (Total value of all companies in Chulwalar)
```{r}
#plot(ChulwalarIndex, main="ChulwalarIndex")
#cor(TotalAsIs, ChulwalarIndex)
```  



* Monthly Inflation rate in Chulwalar  
```{r}
#plot(Inflation, main="Inflation")
#cor(TotalAsIs, Inflation)
```  



*	Proposed spending for National Holidays
```{r}
#plot(IndependenceDayPresents, main="IndependenceDayPresents")
#cor(TotalAsIs, IndependenceDayPresents)
```  
The indicators will be converted into individual  vectors and subsequently converted into time series. The correlation of the indicators will then be tested against the As Is exports for Chulwalar. 




###Forecasting models

* Ses : Simple Exponential Smoothing model
* Holts Model  
* Holts Winter Model  

