---
title: "Forecasting Models"
author: "Vishal & Blake"
date: "July 24, 2016"
output: 
  html_document:
      keep_md:  true
---


* *Setting current working directory to Analysis folder*  
    ```{r echo=FALSE}  
      #getwd()  
      # Setting current working directory to Analysis folder so we can access files in this folder directly.  
      setwd('../Analysis')  
    ```  

* *Loading knitr library*  

```{r echo=FALSE}
#Load knitr and fpp library
library(knitr)
```  

* *Seeting chunk options and reading chunks from R scripts*  
```{r echo=FALSE}
#Setting chunk options before reading R script with knitr chunks.
opts_chunk$set(echo = FALSE, cache=FALSE)

#Read chunks from R Script file here
read_chunk('ForecastCode.R')
#read_chunk('Test.R')

```  
  
```{r ForecastModels, echo=FALSE}

```

#1. Plot SES model

* *Simple Exponential Smoothing* : In this type of model, forecast are calculated using averages from past values. Weight on average values reduce as values become older in timeseries.  We will plot a Simple Exponential Smoothing chart for "TotalAsIs" timeseries that contains observed data. Simple Exponential Smoothing can be used in case there is no trend and/or seasonal component in the data.  

*In below plot we are forecasting 12 values using SES model.*  


```{r echo=FALSE}
plot(Model_ses, plot.conf=FALSE, ylab="Exports Chulwalar  )", xlab="Year", main="", fcol="white", type="o")
lines(fitted(Model_ses), col="green", type="o")
lines(Model_ses$mean, col="blue", type="o")
legend("topleft",lty=1, col=c(1,"green"), c("data", expression(alpha == 0.671)),pch=1)

#summary(Model_ses)
```


* *Holt's various models (linear, exponential, damped, damped with exponential)

    * Linear Trend  
    ```{r echo=FALSE}
    #summary(Model_holt_1)
    plot(Model_holt_1)
    plot(Model_holt_1$model$state)
    ```

    * Exponential Trend  
    ```{r echo=FALSE}
    #summary(Model_holt_2)
    plot(Model_holt_2)
    plot(Model_holt_2$model$state)
    ```
    
    * Dampened Trend  
    ```{r echo=FALSE}
    #summary(Model_holt_3)
    plot(Model_holt_3)
    plot(Model_holt_3$model$state)
    ```
    
    * Dampened with Exponential Trend  
    ```{r echo=FALSE}
    #summary(Model_holt_4)
    plot(Model_holt_4)
    plot(Model_holt_4$model$state)
    ```
    
    

# Combined Chart for all models  

```{r echo=FALSE}
plot(Model_holt_1, plot.conf=FALSE, ylab="Exports Chulwalar  )", xlab="Year", main="", fcol="white", type="o")
lines(fitted(Model_ses), col="purple", type="o")
lines(fitted(Model_holt_1), col="blue", type="o")
lines(fitted(Model_holt_2), col="red", type="o")
lines(fitted(Model_holt_3), col="green", type="o")
lines(fitted(Model_holt_4), col="orange", type="o")
lines(Model_ses$mean, col="purple", type="o")
lines(Model_holt_1$mean, col="blue", type="o")
lines(Model_holt_2$mean, col="red", type="o")
lines(Model_holt_3$mean, col="green", type="o")
lines(Model_holt_4$mean, col="orange", type="o")
legend("topleft",lty=1, col=c(1,"purple","blue","red","green","orange"), c("data", "SES","Holts auto", "Exponential", "Additive Damped", "Multiplicative Damped"),pch=1)
```



    
    
    
    