---
title: "Summary"
author: "Vishal & Blake"
date: "July 24, 2016"
output: 
  html_document:
          keep_md:  true
---

# Reading previous source files  

```{r echo=FALSE}  
      #getwd()  
      # Setting current working directory to Analysis folder so we can access files in this folder directly.  
      setwd('../Paper')  
      library(knitr)
      library(ggplot2)
      opts_chunk$set(echo = FALSE, cache=FALSE)
      read_chunk('SummaryCode.R')
```  

```{r SummaryCode, echo=FALSE}

```

# Comparing AIC, AICc and BIC for all the models

Below 3 separate graphs show plots for AIC, AICc and BIC for all the models. After looking at them, the min AICc , min AICc and min BIC, all are from Holt Winter's additive model.
Hence, it appears that Holt Winters Additive model is the **best model** to choose for forecasting exports in 2014.


```{r }
  ggplot(stat_df, aes(x=ModelName, y=AIC, fill=ModelName)) + geom_bar(stat='identity',width=0.5, position="dodge")  
  ggplot(stat_df, aes(x=ModelName, y=AICc, fill=ModelName)) + geom_bar(stat='identity',width=0.5, position="dodge")  
  ggplot(stat_df, aes(x=ModelName, y=BIC, fill=ModelName)) + geom_bar(stat='identity',width=0.5, position="dodge")  
```
    
# Final Forecast for 2014 Exports 

```{r echo=FALSE}
plot(Model_hw_1, ylab="( Exports Chulwalar )", plot.conf=FALSE, type="o", fcol="white", xlab="Year", main="Holt-Winters' Additive Forecasts")
lines(fitted(Model_hw_1), col="red", lty=2)
lines(Model_hw_1$mean, type="o", col="red")
legend("topleft",lty=1, pch=1, col=1:3, c("data","Holt Winters' Additive"))
```  
    